The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2017-11-14 paper/ms.tex
Minor edits to paper

A number of the simulations have been run using an N-body code to represent the collisionless dark matter component of the cluster via massive particles. A number of these dark matter particles can be sampled from the simulation to represent mock ``galaxies,'' which can also be treated as a collisionless component. For some of these simulations, we have created mock galaxy catalogs.

@@

A ds9 region file containing point regions corresponding to the galaxy positions is provided for each epoch and line-of-sight in addition to the FITS file, which allows the galaxy positions to be plotted over the projections of the other fields.

>>>>

A number of the simulations have been run using an N-body code to represent the collisionless dark matter component of the cluster via massive particles. A number of these dark matter particles can be sampled from the simulation to represent mock ``galaxies,'' which can also be treated as a collisionless component. For some of these simulations, we have created mock galaxy catalogs, {\bf which consist of the sky positions and redshifts of ``galaxy'' particles.}

@@

A ds9 region file containing point regions corresponding to the galaxy positions is provided for each epoch and line-of-sight in addition to the FITS file, which allows the galaxy positions to be plotted over the projections of the other fields. {\bf At the time of writing, mock galaxy catalogs have been created for the ``A Parameter Space Exploration of Galaxy Cluster Merger'' simulations found at \url{http://gcmc.hub.yt/fiducial/index.html}, an example of which may be found at \url{http://gcmc.hub.yt/fiducial/1to1_b0.5/0139.html}, under the heading ``Galaxies''.}
